---
title: "rtweet Sentiment Analysis"
author: "Matthew Hendrickson"
date: "4/20/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Getting Started

To start any project, we first need to set up the environment.

The following libraries are used through this project.

```{r packages, message=FALSE, warning=FALSE}
library("rtweet")
library("tidyverse")
library("scales")
library("skimr")
```



# Getting Twitter Data

## Selecting the object of analysis

The first step is to evaluate handles and hashtags to ensure there is enough data available for analysis.

I'll start with the following and get the record counts for each:
1. Myself - [@mjhendrickson](https://twitter.com/mjhendrickson)
2. R Ladies Global, which is an incredibly supportive organization - [@RLadiesGlobal](https://twitter.com/RLadiesGlobal)
3. RStudio, the fantastic R IDE - 
[@rstudio](https://twitter.com/rstudio)

```{r mh record count}
mh_test <- get_timeline('mjhendrickson', n = 1)
           mh_test$statuses_count
```

```{r rl record count}
rl_test <- get_timeline('RLadiesGlobal', n = 1)
           rl_test$statuses_count
```

```{r rs record count}
rs_test <- get_timeline('rstudio', n = 1)
           rs_test$statuses_count
```

```{r rstats record count}
rstats_test <- search_tweets('#rstats', n = 1)
               rstats_test$statuses_count
```

To play it safe, I'll begin this analysis with myself.



## Pulling the data

The data pull will involve pulling the timeline for [@mjhendrickson](https://twitter.com/mjhendrickson).

```{r mh data pull}
mh <- get_timeline('mjhendrickson', n = 5000) # 5000 ensures all records are taken
```

## Contents of the data

The data itself consists of the following fields:

```{r mh available fields}
print(colnames(mh))
```

Each field can be evaluated individually. Before that step is taken, a tool such as `DataExplorer` can be useful as it provides a fast first-pass at exploratory data analysis (EDA).

```{r mh skim}
skim(mh)
```

